PAO

### 2021-05-20 doc/sand/pao.tex

\begin{sphinxadmonition}{note}{Note:}
PAO solvers cannot currently solve trilevel solvers like this,
but an issue has been submitted to add this functionality.
\end{sphinxadmonition}

@@

@@

\section{Solvers}
\label{\detokenize{solvers:solvers}}\label{\detokenize{solvers::doc}}
After formulating a multilevel problem, PAO users will generally need to
(1) transform the model to a standard form, and (2) apply an optimizer
to solve the problem.  The examples in the previous sections illustrate
that step (1) is often optional;  PAO automates the applications of
several model transformations, particularly for problems formulated with
Pyomo.  The following section summarizes the solvers available in PAO,
and describes how PAO manages solvers Section \DUrole{xref,std,std-ref}{transformations}
describes model transformations in PAO.

@@

\begin{sphinxadmonition}{note}{Note:}
The iterface to MibS is a prototype that has not been well\sphinxhyphen{}tested.
This interface will be documented and finalized in an upcomgin next
release of PAO.
\end{sphinxadmonition}

@@

\begin{sphinxadmonition}{warning}{Warning:}
The \sphinxcode{\sphinxupquote{solve()}} current passes unknown keyword arguments to the
optimize used by PAO solvers, but this feature will be disabled.
\end{sphinxadmonition}

@@

This function generates a {\hyperref[\detokenize{reference/mpr:pao.mpr.repn.LinearMultilevelProblem}]{\sphinxcrossref{\sphinxcode{\sphinxupquote{LinearMultilevelProblem}}}}} or
{\hyperref[\detokenize{reference/mpr:pao.mpr.repn.QuadraticMultilevelProblem}]{\sphinxcrossref{\sphinxcode{\sphinxupquote{QuadraticMultilevelProblem}}}}} from a Pyomo model.  By default,
all constrints in the MPR representation are inequalities.
\end{quote}

@@

This function generates an equivalent linear multilevel representation for which all
variables are non\sphinxhyphen{}negative and all constraints have the same form (inequalities or equalities).
This simplifies the formulation of solvers, which typically assume a standard form
for subproblems.
\end{quote}

>>>>

\begin{sphinxadmonition}{note}{Note:}
PAO solvers cannot currently solve trilevel problems like this,
but an issue has been submitted to add this functionality.
\end{sphinxadmonition}

@@

In general, it may be difficult to determine a valid value of $M$.   Thus, this transformation may
result in a restriction or relaxation of the original problem (depending on where the big-M values
are introduced).

@@

\section{Solvers}
\label{\detokenize{solvers:solvers}}\label{\detokenize{solvers::doc}}
After formulating a multilevel problem, PAO users will generally need to
(1) transform the model to a standard form, and (2) apply an optimizer
to solve the problem.  The examples in the previous sections illustrate
that step (1) is often optional;  PAO automates the applications of
several model transformations, particularly for problems formulated with
Pyomo.  The following section summarizes the solvers available in PAO,
and describes how PAO manages solvers. Section \DUrole{xref,std,std-ref}{transformations}
describes model transformations in PAO.

@@

\begin{sphinxadmonition}{note}{Note:}
The iterface to MibS is a prototype that has not been well\sphinxhyphen{}tested.
This interface will be documented and finalized in an upcoming
release of PAO.
\end{sphinxadmonition}

@@

\begin{sphinxadmonition}{warning}{Warning:}
The \sphinxcode{\sphinxupquote{solve()}} current passes unknown keyword arguments to the
optimizer used by PAO solvers, but this feature will be disabled.
\end{sphinxadmonition}

@@

This function generates a {\hyperref[\detokenize{reference/mpr:pao.mpr.repn.LinearMultilevelProblem}]{\sphinxcrossref{\sphinxcode{\sphinxupquote{LinearMultilevelProblem}}}}} or
{\hyperref[\detokenize{reference/mpr:pao.mpr.repn.QuadraticMultilevelProblem}]{\sphinxcrossref{\sphinxcode{\sphinxupquote{QuadraticMultilevelProblem}}}}} from a Pyomo model.  By default,
all constraints in the MPR representation are inequalities.
\end{quote}

@@

This function generates an equivalent linear multilevel representation for which all
variables are non\sphinxhyphen{}negative and all constraints have the same form (inequalities or equalities).
This simplifies the implementation of solvers, which typically assume a standard form
for subproblems.
\end{quote}
